A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-09 final project/Manuscript.Rmd
Updated final with more lit review

---
title             : "A Logistic Regression Qpproach to CoIL Challenge 2000"
shorttitle        : " "
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

Participants used a variety of approaches in formulating their submissions including: Artificial Neural Networks [@Kim], Naïve Bayes [@Elkan].

@@

<!--
Other solutions (in alphabetical order):

3 Achim Lewandowski. How to detect potential customers. [ps.gz], [pdf]

4 Alexander Seewald. CoIL Challenge 2000 Submitted Solution. [ps.gz], [pdf]

5 A.P. White and W.Z. Liu. The CoIL Challenge: an Application of Classification Trees with Bootstrap Aggregation. [ps.gz], [pdf]

6 Andrew Greenyer. Coil 2000 Competition. The use of a learning classifier system JXCS. [ps.gz], [pdf]

7 Arnold Koudijs. CoIL Challenge 2000 Submission for the Description Task. [ps.gz], [pdf]

8 William M. Crocoll. Artificial Neural Network Portion of Coil Study. [ps.gz], [pdf]

9 Chris Leckie and Herman Ferra. COIL Challenge 2000 Description Task. [ps.gz], [pdf]

10 Gustavo Denicolay and Gaston Morales. CoIL Challenge 2000 Submission for the Description Task. [ps.gz] [pdf]

11 Dragan Gamberger. Solution based on ILLM confirmation rule. [ps.gz], [pdf]

>>>>

---
title             : "A Logistic Regression Approach to CoIL Challenge 2000"
shorttitle        : " "
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

Participants used a variety of approaches in formulating their submissions including:

- Classification Trees with Bagging [@White];

- C4.5 [@Seewald];

- Evolutionary Algorithm [@Koudijs];

- Inductive Learning by Logic Minimization (ILLM) [@Gamberger];

- Mask Perceptron with Boosting [@Leckie];

- Naïve Bayes [@Elkan]; and

- Neural Networks[@Crocoll], [@Kim];

- Scoring System [@Lewandowski];

- Support Vector Machines; and

- XCS [@Greenyer].

@@

<!--
10 Gustavo Denicolay and Gaston Morales. CoIL Challenge 2000 Submission for the Description Task. [ps.gz] [pdf] - Not sure what they used

### 2019-11-09 final project/Manuscript.tex
Updated final with more lit review

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={A Logistic Regression Qpproach to CoIL Challenge 2000},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{A Logistic Regression Qpproach to CoIL Challenge 2000}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

@@

Researchers used a variety of approaches in formulating their submissions including: Artificial Neural Networks (Kim \& Street, 2000), Naïve Bayes (Elkan, 2000).

@@

The maximum number of policyowners that could be found was 238, the winning model selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks)and 118 (linear!) policy owners. (Putten et al., 2000)

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Elkan}{}%
Elkan, C. (2000). CoIL challenge 2000 entry. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/ELKANP~1.pdf}

@@

@@

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={A Logistic Regression Approach to CoIL Challenge 2000},
            pdfauthor={Corey Arnouts, Adam Douglas, Jason Givens-Doyle, \& Michael Silva},
            pdfkeywords={CoIL Challenge, Logistic Regression},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{A Logistic Regression Approach to CoIL Challenge 2000}
    \author{Corey Arnouts\textsuperscript{1}, Adam Douglas\textsuperscript{1}, Jason Givens-Doyle\textsuperscript{1}, \& Michael Silva\textsuperscript{1}}
    \date{}

@@

Participants used a variety of approaches in formulating their submissions including:

\begin{itemize}
\item
  Classification Trees with Bagging (White \& Liu, 2000);
\item
  C4.5 (Seewald, 2000);
\item
  Evolutionary Algorithm (Koudijs, 2000);
\item
  Inductive Learning by Logic Minimization (ILLM) (Gamberger, 2000);
\item
  Mask Perceptron with Boosting (Leckie \& Ferra, 2000);
\item
  Naïve Bayes (Elkan, 2000); and
\item
  Neural Networks(Crocoll, 2000), (Kim \& Street, 2000);
\item
  Scoring System (Lewandowski, 2000);
\item
  Support Vector Machines; and
\item
  XCS (Greenyer, 2000).
\end{itemize}

The maximum number of policyowners that could be found was 238. The winning model (Elkan, 2000) selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear!) policy owners. (Putten et al., 2000)

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Crocoll}{}%
Crocoll, W. M. (2000). Artificial neural network portion of coil study. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/CROCOL~1.pdf}

\leavevmode\hypertarget{ref-Elkan}{}%
Elkan, C. (2000). CoIL challenge 2000 entry. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/ELKANP~1.pdf}

\leavevmode\hypertarget{ref-Gamberger}{}%
Gamberger, D. (2000). Solution based on illm confirmation rule. Retrieved from \url{http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/GAMBER~1.pdf}

\leavevmode\hypertarget{ref-Greenyer}{}%
Greenyer, A. (2000). Coil 2000 competition. The use of a learning classifier system jxcs. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/GREENY~1.pdf}

@@

\leavevmode\hypertarget{ref-Koudijs}{}%
Koudijs, A. (2000). CoIL challenge 2000 submission for the description task. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/KOUDIJ~1.pdf}

\leavevmode\hypertarget{ref-Leckie}{}%
Leckie, C., \& Ferra, H. (2000). COIL challenge 2000 description task. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/LECKIE~1.pdf}

\leavevmode\hypertarget{ref-Lewandowski}{}%
Lewandowski, A. (2000). How to detect potential customers. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/LEWAND~1.pdf}

@@

\leavevmode\hypertarget{ref-Seewald}{}%
Seewald, A. (2000). CoIL challenge 2000 submitted solution. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/SEEWAL~1.pdf}

\leavevmode\hypertarget{ref-White}{}%
White, A. P., \& Liu, W. Z. (2000). The coil challenge: An application of classification trees with bootstrap aggregation. Retrieved from \url{http://www.liacs.nl/~putten/library/cc2000/WHITEP~1.pdf}
